Preprocessing

### 2023-08-01 docs/presentation/preprocess.Rmd
viz: refactor 5 levels to 4

## Bar charts
Order Q5 and Q7 responses
```{r}
analysis %<>%
  mutate(across(all_of(four_level_cols), ~ factor(., levels = four_levels))) %>%
  mutate(across(all_of(five_level_cols), ~ factor(., levels = five_levels)))
```

>>>>

## Bar charts
Cast 5 levels to 4
```{r eval=FALSE, include=FALSE}
analysis %<>%
  mutate(
    across(
      all_of(five_level_cols),
      ~ case_when(
        . == "Never" ~ "Not at all",
        . == "Rarely" ~ "Very little",
        . == "Some of the time" ~ "Somewhat",
        . %in% c("Most of the time", "Always") ~ "To a great extent"
      )
    )
  )
```

Order Q5 and Q7 responses
```{r}
analysis %<>%
  mutate(across(all_of(four_level_cols), ~ factor(., levels = four_levels))) %>%
  mutate(across(all_of(five_level_cols), ~ factor(., levels = four_levels)))
```
